Impacts of the exclusion of scientific surveys from closed areas on population indices, stock assessment, and conservation

### 2021-08-26 paper/paper.Rmd
Indices
https://trends.google.com/trends/explore?q=indices,indexes

```{r, out.width="\\textwidth", fig.cap="HBLL N indexes calculated from a geostatistical model."}
include_graphics(here("figs/index-hbll-geo-restricted.pdf"))
```

@@

```{r, out.width="5in", fig.cap="HBLL N indexes: ratio of the restricted to the original index CV. Dots represent the mean CV ratio and line segments represent the lower and upper ratios across years."}
include_graphics(here("figs/index-geo-hbll-cv-ratio-dotplot.pdf"))
```

@@

```{r, out.width="0.72\\textwidth", fig.cap="Synoptic trawl survey indexes calculated from a geostatistical model."}
include_graphics(here("figs/index-syn-geo-restricted-highlight.pdf"))
```

>>>>

```{r, out.width="\\textwidth", fig.cap="HBLL N indices calculated from a geostatistical model."}
include_graphics(here("figs/index-hbll-geo-restricted.pdf"))
```

@@

```{r, out.width="5in", fig.cap="HBLL N indices: ratio of the restricted to the original index CV. Dots represent the mean CV ratio and line segments represent the lower and upper ratios across years."}
include_graphics(here("figs/index-geo-hbll-cv-ratio-dotplot.pdf"))
```

@@

```{r, out.width="0.72\\textwidth", fig.cap="Synoptic trawl survey indices calculated from a geostatistical model."}
include_graphics(here("figs/index-syn-geo-restricted-highlight.pdf"))
```
